Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-12 man/ms.Rmd
comentario radial growth

Las sequías produjeron reducciones de crecimiento en los tres sitios. De los eventos de sequía analizados, destaca por un lado que 1995 produjo la mayor reducción de crecimiento.

VAS POR AQUI 
For 2005 and 2012 we found a greater reduction of RWI for northern site (SJ) but weaker for southern sites (CA-High and CA-Low). Yet, the lowest pointer year (*i.e.* the lowest growth) since 1950 was 1995 in all chronologies (Figure S3).

>>>>

From a long-term perspective, drought events produced reduction of RWI for all sites (Figure S3), particularly in 1995 drought, when the greatest reduction of tree-growth were recorded for all chronologies. Southern sites (CA-High and CA-Low) showed weaker reductions than northern site (SJ), especially for 2005 and 2012 (Figure S3). Trees from northern site also suffered a great reduction during 1945-1946 drought event.
